---
title: "Run Logica"
author: "borangao"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

# Installation of Logica

```{r,message=FALSE,warning=FALSE}
library(devtools)
# Install Logica
install_github("borangao/Logica",dependencies = FALSE)
# Load Logica
library(Logica)
```

# Logica Example
## 1. Data Formatting for Logica:

Use the example from Data preparation.

```{r,message=FALSE, warning=FALSE}
library(data.table)
library(Logica)
block_index = 1
trait = "LDL"
ancestry_1 = "EUR"
ancestry_2 = "EAS"
z1<-fread(file.path("/net/fantasia/home/borang/MALGC/pipeline_example/LDL/LDL_Block",paste0(trait , "_",ancestry_1,"_block_",block_index ,".txt")))
z2<-fread(file.path("/net/fantasia/home/borang/MALGC/pipeline_example/LDL/LDL_Block",paste0(trait , "_",ancestry_2,"_block_",block_index ,".txt")))
load(file.path("/net/fantasia/home/borang/MALGC/pipeline_example/LDL/LD_ref",paste0("LD_",block_index ,".RData")))
load(file.path("/net/fantasia/home/borang/MALGC/pipeline_example/LDL/LDL_Block",paste0(trait,"_intercept.RData")))

preprocess_data_file<-preprocess_data(z1,z2,ancestry_1_cov,ancestry_2_cov)
```

## 2. Run Logica:
```{r,message=FALSE, warning=FALSE}
logica_res<-run_Logica(preprocess_data_file$pop1$z,preprocess_data_file$pop2$z, preprocess_data_file$pop1$R, preprocess_data_file$pop2$R, median(preprocess_data_file$pop1$z$N), 
                        median(preprocess_data_file$pop2$z$N), 
                        z1_intercept = ancestry_1_lder_intercept, z2_intercept = ancestry_2_lder_intercept, fix_intercept = TRUE)
```

### Logica Result Interpretation:
```{r,message=FALSE, warning=FALSE}
print(logica_res)
```

**Logica Result Interpretation:**

- **chr**: Chromosome identifier for the genomic region analyzed.
- **start** and **end**: Genomic coordinates marking the start and end positions of the analyzed region.
- **Est_h2_1**: Estimated heritability for ancestry 1, indicating the proportion of phenotypic variance explained by genetic factors within this region.
- **Est_h2_2**: Estimated heritability for ancestry 2, interpreted similarly to Est_h2_1.
- **Est_cov**: Estimated genetic covariance between ancestry 1 and ancestry 2, measuring the degree of shared genetic influence.
- **Est_rho**: Estimated genetic correlation derived from covariance (Est_cov), standardized by heritabilities, quantifying genetic similarity across ancestries.
- **P_h2_1**: P-value testing if heritability for ancestry 1 differs significantly from zero.
- **P_h2_2**: P-value testing if heritability for ancestry 2 differs significantly from zero.
- **P_rho_score**: Score-based test P-value assessing the significance of genetic correlation.
- **P_rho_LLK**: Likelihood-based test P-value assessing the significance of genetic correlation.

> **Note:** We also provided code for submitting slurm array jobs to enable parallele computing Step4_Logica.R and Step4_Logica.sh

## 3. Testing Composite Null Hypothesis

 The composite null hypothesis is constructed by combining the individual null hypotheses from each genomic region.
 
```{r,message=FALSE, warning=FALSE}
setwd("/net/fantasia/home/borang/MALGC/pipeline_example/LDL_Block")
list.files(pattern = "Logica_res_LDL_block") -> file_list
library(data.table)
all_file<-c()
for(file in file_list){
  logica_res<-fread(file)
  all_file<-rbind(all_file,logica_res)
}

all_file$p_h2_HDMT<-p_HDMT(all_file$P_h2_1,all_file$P_h2_2)
head(all_file,10)
```
